### 2025-07-06 index.qmd
20250705 - tweaks
20250705 - log chunk execution times

>>>>

```{r}
#| label: setup
#| include: false
#| message: !expr NA

# Preface

# Globally apply message = NA (https://github.com/quarto-dev/quarto-cli/discussions/7443)
knitr::opts_chunk$set(
  time = TRUE,
  message = NA # show messages in console but not book
)

# Null coalescing operator
`%||%` <- function(a, b) if (!is.null(a)) a else b

# Prepare log file
log_file <- "chunk-times.txt"
if (file.exists(log_file)) file.remove(log_file)

# Timing hook
knitr::knit_hooks$set(time = function(before, options) {
  if (before) {
    options$start_time <- Sys.time()
  } else {
    elapsed <- difftime(Sys.time(), options$start_time, units = "secs")
    label <- options$label %||% "<unnamed>"
    msg <- sprintf("Chunk `%s` ran in %.2f seconds.", label, as.numeric(elapsed))

    # Log to GitHub Actions console
    message(sprintf("::notice title=Chunk Time::%s", msg))

    # Also save to file
    cat(msg, file = log_file, append = TRUE, sep = "\n")
  }
})
```
